Precision calculations of the cosmic shear power spectrum projection

### 2017-04-24 limber2.tex
undefined reference fixed

\renewcommand{\baselinestretch}{1.5}
\begin{table}
\begin{centering}
  %
  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. `ID' is the label
    used in the text and figures.
    The third column shows the power-spectrum pre-factor $p(\ell)$. } 
    %
    \begin{tabular}{|p{0.22\textwidth}|l|c|c|c|c|c|p{0.21\textwidth}}
  \hline
  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & \forref{$\ell_{0.1}$} & \forref{$\ell_{0.01}$} & Comment \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat & L1Fl & (\ref{eq:P_ell_limber1})+(i)
    & $1$ & $\ell$ & $4$ & $60$ & Pre-2014 CFHTLenS and DLS \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat & ExtL1Fl & (\ref{eq:P_ell_limber1})+(ii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat & ExtL1FlHyb & (\ref{eq:P_ell_limber1})+(iii)
    & $1$ & $\ell + \frac 1 2$ & & & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & & & \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat & ExtL2Fl &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ 
    & $\ell+\frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  %
  $2^{\rm st}$-order extended Limber, hybrid, flat & ExtL2FlHyb &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
    & $1$ 
    & $\ell+ \frac 1 2$ & & & Best flat-sky approximation \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & & & Best approximation \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      - & - & - & - & Correct projection \\ \hline
  %
  \end{tabular}

@@

The spherical power spectrum is formally not defined for non-integer $\ell$
\citep[see][for alternative spherical-sky formulae for the two-point
correlation function]{2005PhRvD..72b3516C}, as functions defined on the
sphere are necessarily periodic.
As we have shown in section~\ref{sec:comp}, however, the spherical second-order
extended Limber approximation provides a percent-level precision representation
of the full spherical projection for $\ell > 3$.
The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
thus use the spherical power spectrum with
the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
functions. This has the advantage being able to employ fast FFT numerical implementations of
the Hankel tranforms \citep{fftlog}, when Monte-Carlo sampling.

We compare predictions for the two-point shear correlation function using
the Hankel transformation and the full spherical transformation in
Fig.~\ref{fig:xi_p_wigner}. We show the full projection and the best
approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
%
We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
%
The difference between the second-order Limber and full projection solution using the
spherical transform (equation~\ref{eq:xi_wigner}) is well below one percent
for $\vartheta < 200$ arcminutes.
The red circles in Fig.~\ref{fig:xi_p_wigner} present the limit of
precision that we can achieve with the current fast Hankel transform implementation
for the correlation function. The green line shows the limit of the
second-order Limber approximation on the correlation function.

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_wigner}
      \hspace*{2em}
      \includegraphics{figures/xi_p_wigner_delta}
    }
  \end{center}

  \caption{\emph{Left panel \mk{Needs to be updated}:} The shear correlation function component $\xi_+$
for the ExtL2Sph projection using the spherical transform (green line for
ExtL2Sph, grey squares for FullSph), compared to the flat-sky Hankel transform
of ExtL2Sph (red circles). \emph{Right panel:} The relative difference compared
to the full spherical case FullSph of ExtL2Sph with spherical transform (green
line), and Hankel transform (red circles).}

>>>>

\renewcommand{\baselinestretch}{1.5}
\begin{table}
\begin{centering}
  %
  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. `ID' is the label
    used in the text and figures.
    \forref{The sixth (seventh) column indicates the mode $\ell_x$ such that for $\ell \leq \ell_x$, the approximated
    power spectrum is more accurate than $x$, with $x=0.1$ ($0.01$).}
    } 
    %
    \begin{tabular}{|p{0.22\textwidth}|l|c|c|c|c|c|p{0.21\textwidth}}
  \hline
  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & \forref{$\ell_{0.1}$} & \forref{$\ell_{0.01}$} & Comment \\ \hline
  %  black
  $1^{\rm st}$-order standard Limber, flat & L1Fl & (\ref{eq:P_ell_limber1})+(i)
    & $1$ & $\ell$ & $4$ & $60$ & Pre-2014 CFHTLenS and DLS \\ \hline
  % blue
  $1^{\rm st}$-order extended Limber, flat & ExtL1Fl & (\ref{eq:P_ell_limber1})+(ii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & $20$ & $200$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  % pink
  $1^{\rm st}$-order extended Limber, hybrid, flat & ExtL1FlHyb & (\ref{eq:P_ell_limber1})+(iii)
    & $1$ & $\ell + \frac 1 2$ & $4$ & $10$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
  % cyan
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & $3$ & $12$ & \\ \hline
  % grey
  $2^{\rm st}$-order extended Limber, flat & ExtL2Fl &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
    & $\frac{\ell^4}{(\ell+1/2)^4}$ 
    & $\ell+\frac 1 2$ & $19$ & $200$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
  % orange
  $2^{\rm st}$-order extended Limber, hybrid, flat & ExtL2FlHyb &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
    & $1$ 
    & $\ell+ \frac 1 2$ & $5$ & $16$ & Best flat-sky approximation \\ \hline
  % green
  $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & $2$ & $5$ & Best approximation \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      - & - & - & - & Correct projection \\ \hline
  %
  \end{tabular}

@@

The spherical power spectrum is formally not defined for non-integer $\ell$
\citep[see][for alternative spherical-sky formulae for the two-point
correlation function]{2005PhRvD..72b3516C}, as functions defined on the
sphere are necessarily periodic.
As we have shown in section~\ref{sec:comp}, however, the spherical second-order
extended Limber approximation provides a percent-level precision representation
of the full spherical projection for $\ell > 3$.
The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
thus use the spherical power spectrum with
the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
functions. This has the advantage being able to employ fast FFT numerical implementations of
the Hankel tranforms \citep{2000MNRAS.312..257H}, when Monte-Carlo sampling.

We compare predictions for the two-point shear correlation function using
the Hankel transformation and the full spherical transformation in
Fig.~\ref{fig:xi_p_wigner}. We show the full projection and the best
approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
%
We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than \forref{$5$ ($0.2$) percent
for $\xi_+$ ($\xi_-$)}.
%
The difference between the second-order Limber and full projection solution using the
spherical transform (equation~\ref{eq:xi_wigner}) is well below one \forref{($0.03$) percent
on scales of $\vartheta < 300$ arcminutes for $\xi_+$ ($\xi_-$)}.
The red lines in Fig.~\ref{fig:xi_p_wigner} present the limit of
precision that we can achieve with the current fast Hankel transform implementation
for the correlation function. The green \forref{lines show} the limit of the
second-order Limber approximation on the correlation function.

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_wigner_delta}
      \hspace*{2em}
      \includegraphics{figures/xi_m_wigner_delta}
    }
  \end{center}

  \caption{%
    \forref{The difference of the two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right})
    of the ExtL2Sph projection relative to the full spherical case (FullSph). Two cases of the shear correlation function transformation for
    ExtL2Spha are shown,
    the full spherical case (eq.~\ref{eq:xi_wigner}, green solid lines), and the flat-sky Hankel transform (eq.~\ref{eqn:xiGG}, red dashed curves).}
  }
